Automated Topic Naming

### 2012-03-19 ese/ese.tex
updated figure 7 with dashed lines

%\subsubsection{Analysis of the Semi-unsupervised Labelling} %--- %Based
				%on the labels, and our manual topic
				%labelling, 
%\noindent \textbf{Analysis of the unsupervised labelling} --- %Based on the labels, and our manual topic labelling, 
%we compared the results of the unsupervised word matching approach. 
For each quality in the high-level ISO 9126 taxonomy (namely, \emph{Maintainability, Usability, Reliability, Efficiency, Portability, Functionality}) we assessed whether the semi-unsupervised labels for a topic matched the manual annotations we created for the validation corpus. 
Recall that the manual annotations were not used to
train the labelling process.
As described in Section \ref{sec:wordlist} we used both ROC and F-measure measures to evaluate the performance of the classification.
Figure \ref{fig:maxdb-unsup-results} shows our ROC results for
PostgreSQL, MaxDB and MySQL. We omit plots of \textsf{exp1} due to poor results. We describe F-measure results in the text below.

@@

\begin{figure}
  \centering
  \includegraphics[width=.9\textwidth]{figures/postgresql-author-cluster}
  \caption{PostgreSQL Author Clusters: Authors clustered by Euclidean
    distance of their NFR contributions. The outer rectangles (black)
    reflect the clustering of authors into 2 clusters; while the inner rectangles
    (dim grey) reflect clustering of authors into 6 clusters. The height is a
    measure of cluster similarity, Euclidean distance, where smaller
    values are more similar. Individuals that share
    branches are more similar to each other individuals who do
    not. The longer the path, in terms of height, between two
    individuals, the more different their NFR contributions are.}
\label{fig:authorcluster}
\end{figure}

>>>>

%\subsubsection{Analysis of the Semi-unsupervised Labelling} %--- %Based
				%on the labels, and our manual topic
				%labelling, 
%\noindent \textbf{Analysis of the unsupervised labelling} --- %Based on the labels, and our manual topic labelling, 
%we compared the results of the unsupervised word matching approach. 
For each quality in the high-level ISO 9126 taxonomy (namely, \emph{Maintainability, Usability, Reliability, Efficiency, Portability, Functionality}) we assessed whether the semi-unsupervised labels for a topic matched the manual annotations we created for the validation corpus. 
Recall that the manual annotations were not used to
train the labelling process.
As described in Section \ref{sec:wordlist} we used both ROC and F-measure measures to evaluate the performance of the classification.
Figure \ref{fig:maxdb-unsup-results} shows our ROC results for
PostgreSQL, MaxDB and MySQL. We did not calculate the ROC of \textsf{exp1} because the labels used were completely different than the manual annotation labels. We describe F-measure results in the text below.

@@

\begin{figure}
  \centering
  \includegraphics[width=.9\textwidth]{figures/postgresql-author-cluster}
  \caption{PostgreSQL Author Clusters: Authors clustered by Euclidean
    distance of their NFR contributions. The two outer rectangles (thicker black)
    reflect the clustering of authors into 2 clusters; while the inner rectangles
    (dashed) reflect clustering of authors into 6 clusters. The height is a
    measure of cluster similarity, Euclidean distance, where smaller
    values are more similar. Individuals that share
    branches are more similar to each other individuals who do
    not. The longer the path, in terms of height, between two
    individuals, the more different their NFR contributions are.}
\label{fig:authorcluster}
\end{figure}
